\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsthm, mathtools}
\usepackage[margin=1in]{geometry}

% Shortcuts
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\set}[1]{\{#1\}}

% Theorem-like environments
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\title{Problem Set 2}
\author{Michael Duren}
\date{2026-11-05}

\renewcommand{\thesubsection}{\alph{subsection}}

\begin{document}
\maketitle

\section*{Problem 1}

% PROBLEM 1A =================================================================================================================
\subsection{[3 pts]} \textbf{Theorem:} "Every natural number is tall or wide, but not both." (Proof method: proof by cases.)

\begin{proof}
	The proposition:
	\[
		\forall n \in \N, (\text{Tall}(n) \vee \text{Wide}(n)) \wedge \neg(\text{Tall}(n) \wedge \text{Wide}(n))
	\]
	Let $n \in \N$.

	\textbf{Part 1 (existence):} We WTS $\text{Tall}(n) \wedge \text{Wide}(n)$.
		[TODO: show every natural number is tall or wide].

	\textbf{Part 2(uniqueness):} We WTS $\neg(\text{Tall}(n) \wedge \text{Wide}(n))$ by cases on whether $n$ is tall.
	\begin{itemize}
		\item \emph{Case 1: $n$ is tall.} [TODO: show $n$ is not wide.] Then $\neg (\text{Tall}(n) \wedge \text{Wide}(n))$.
		\item \emph{Case 2: $n$ is not tall.} Then $\text{Tall}(n) \wedge \text{Wide}(n)$ is false because the first conjunct fails.
	\end{itemize}
	Combing Parts 1 and 2 gives the theorem.
\end{proof}

\vspace{1cm}
% END PROBLEM =================================================================================================================

% PROBLEM 1B =================================================================================================================
\subsection{[3 pts]} \textbf{Theorem:} "There exists a happy natural number between 10 and 1000 that has
no happy proper divisors" (Proof method to use: choose 25 as the example)

\begin{proof}
	The proposition $\text{P}$:
	\[
		\exists n \in \N, 10 < n < 1000 \wedge \text{isHappy}(n) \wedge (n \text{ has no happy proper divisors})
	\]
	We claim $n = 25$ satisfies the condition.

	\begin{itemize}
		\item \textbf{Range: } $10 < n < 25$ \checkmark
		\item $n$ itself is happy because [TODO: prove]
		\item $n$ has two proper divisors: $1$ and $5$.

		      \begin{itemize}
			      \item WTS that 1 is not a \underline{happy} number because: [TODO: prove why]
			      \item WTS that 5 is not a \underline{happy} number because: [TODO: prove why]
		      \end{itemize}
	\end{itemize}

	Therefore 25 proves the existential claim, proving the theorem.
\end{proof}

\vspace{1cm}
% END PROBLEM =================================================================================================================

% PROBLEM 1C =================================================================================================================
\subsection{[3 pts]} \textbf{Theorem:} “There are no devious natural numbers.” (Proof method to use: regular induction, with base cases 0 and 1.)
\begin{proof}
	The proposition:
	\[
		\forall n \in \N,\ \neg \text{isDevious}(n)
	\]
	Let $P(n) := \neg \text{isDevious}(n)$. We prove $\forall n \in \N,\ P(n)$ by induction.
	\begin{itemize}
		\item \textbf{Base case $P(0)$:} WTS $0$ is not devious. [TODO]
		\item \textbf{Base case $P(1)$:} WTS $1$ is not devious. [TODO]
		\item \textbf{Inductive step:} Let $n \geq 1$, and assume $P(n-1)$ and $P(n)$. WTS $P(n+1)$.
			      [TODO: using that $n-1$ and $n$ are not devious, show $n+1$ is not devious.]
	\end{itemize}
	By induction, $\forall n \in \N,\ \neg \text{isDevious}(n)$.
\end{proof}

\vspace{1cm}
% END PROBLEM =================================================================================================================

\section*{Problem 2}
% RESET SUB SECTION COUNTER 
\setcounter{subsection}{0}

% PROBLEM 2A =================================================================================================================
\subsection{[3 pts]} Befuddled Brynmor tries to help by proving the claim as follows. What is his mistake?
\begin{proof}
    Brynmor substitutes $x_{i-1} \geq 2^{i-1}$ into $-8 x_{i-1}$ as if it produces a lower bound, but since the coefficient is negative the inequality direction flips: $-8 x_{i-1} \leq -8 \cdot 2^{i-1}$. So his conclusion $x_{i+1} \geq 6 \cdot 2^i - 8 \cdot 2^{i-1}$ is unjustified.
\end{proof}
\vspace{1cm}

\vspace{1cm}
% END PROBLEM =================================================================================================================

% PROBLEM 2B =================================================================================================================
\subsection{[3 pts]} Erroneous Erik tries to help by proving the claim as follows. What is his mistake?\begin{proof}

    Brynmor substitutes $x_{i-1} \geq 2^{i-1}$ into $-8 x_{i-1}$ as if it produces a lower bound, but since the coefficient is negative the inequality direction flips: $-8 x_{i-1} \leq -8 \cdot 2^{i-1}$. So his conclusion $x_{i+1} \geq 6 \cdot 2^i - 8 \cdot 2^{i-1}$ is unjustified.
\end{proof}
\vspace{1cm}

\vspace{1cm}
% END PROBLEM =================================================================================================================


\end{document}
